---
title: "AD data networks"
author: "Anna Liza Kretzschmar"
date: "22/07/2022"
output: html_document
---

Contains images from 5_symptoms-analysis.R

# Heatmaps and networks of symptoms

## Overall symptoms

```{r sympt heat all, echo=FALSE}
heat_all <- "images/sympt-heatmap-all.png"
knitr::include_graphics(heat_all)
```
```{r sympt net all, echo=FALSE}
net_all <- "images/sympt-network-all.png"
knitr::include_graphics(net_all)
```

## Gender difference in symptoms
### Males
```{r sympt heat male, echo=FALSE}
heat_ <- "images/sympt-heatmap-male.png"
knitr::include_graphics(heat_)
```
```{r sympt net male, echo=FALSE}
net_male <- "images/sympt-network-male.png"
knitr::include_graphics(net_male)
```
### Females
```{r sympt heat female, echo=FALSE}
heat_female <- "images/sympt-heatmap-female.png"
knitr::include_graphics(heat_female)
```
```{r sympt net female, echo=FALSE}
net_female <- "images/sympt-network-female.png"
knitr::include_graphics(net_female)
```
### Other genders
```{r sympt heat other_gender, echo=FALSE}
heat_other_gender <- "images/sympt-heatmap-other-gender.png"
knitr::include_graphics(heat_other_gender)
```
```{r sympt net other_gender, echo=FALSE}
net_other_gender <- "images/sympt-network-other-gender.png"
knitr::include_graphics(net_other_gender)
```
### Differential network male and female
```{r sympt netdiff m f, echo=FALSE}
net_diff_m_f <- "images/sympt-network-diff-male-female.png"
knitr::include_graphics(net_diff_m_f)
```

## Cohort difference in symptoms
### Controls
```{r sympt heat cont, echo=FALSE}
heat_control <- "images/sympt-heatmap-control-cohort.png"
knitr::include_graphics(heat_control)
```
```{r sympt net cont, echo=FALSE}
net_control <- "images/sympt-network-control-cohort.png"
knitr::include_graphics(net_control)
```
### Chronic
```{r sympt heat chron, echo=FALSE}
heat_chronic <- "images/sympt-heatmap-chronic-cohort.png"
knitr::include_graphics(heat_chronic)
```
```{r sympt net chron, echo=FALSE}
net_chronic <- "images/sympt-network-chronic-cohort.png"
knitr::include_graphics(net_chronic)
```

### Differential network control and chronic cohorts
```{r sympt netdiff cont chron, echo=FALSE}
net_diff_ <- "images/sympt-network-diff-chron-control.png"
knitr::include_graphics(net_diff_)
```

## Misdiagnosis and diagnosis
### Correct diagnosis
```{r sympt heat cdx, echo=FALSE}
heat_correct_diagnosed <- "images/sympt-heatmap-correct-diagnosed.png"
knitr::include_graphics(heat_correct_diagnosed)
```
```{r sympt net cdx, echo=FALSE}
net_correct_diagnosed <- "images/sympt-network-correct-diagnosed.png"
knitr::include_graphics(net_correct_diagnosed)
```
### Misdagnosis
```{r sympt heat mdx, echo=FALSE}
heat_misdiagnosed <- "images/sympt-heatmap-misdiagnosed.png"
knitr::include_graphics(heat_misdiagnosed)
```
```{r sympt net mdx, echo=FALSE}
net_misdiagnosed <- "images/sympt-network-misdiagnosed.png"
knitr::include_graphics(net_misdiagnosed)
```

### Differential network between correct and misdiagnosis
```{r sympt netdiff mdx cdx, echo=FALSE}
net_diff_mdx_cdx <- "images/sympt-network-diff-mdx-cdx.png"
knitr::include_graphics(net_diff_mdx_cdx)
```
