---
title: "Respondents that wish to be contacted from survey"
author: "Anna Liza Kretzschmar"
date: "19/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook demographics on the respondents from the [Autoimmunity and Health project](https://spoonie-community.netlify.app/) project that consented to be contacted again.

```{r load source file and packages, include = F}
# in 1_1-22_data-clean.R filter for respondents wanting to be contacted:
#insert at line 971 : data.base <- subset(data.base, sex_diff_bool == 1)
#source("2_1-22_Autoimmune-disorder-clean.R")

library(plyr)
library(tidyverse)
library(magrittr)
library(RColorBrewer)
library(wesanderson)
library(ggrepel)
library(arsenal) 
library(ggbeeswarm)
library(wordcloud2)
library(sjlabelled)
library(readxl)
library(viridis)
```
The number of respondents that consent to being contacted for further studies are
```{r count number of respondents, echo=FALSE}
nrow(data.clean)
```
Location of respondents by state:
```{r figure of states,  fig.height = 4, fig.width = 5, fig.align='center', fig.cap="Respondents by state of residence.", echo=FALSE, warning=FALSE}
### pie chart of states
state.count <- data.clean %>%
  count(state) #%>% 
#.[-9, ] #leave in if NAs should be removed
state.count$state2 <- c("ACT", "NSW", "NT", "QLD", "SA", "TAS", "VIC", "WA", "None")

#png("state-summary.png")
ggplot(state.count, aes(x = "", y = n, fill = state2)) +
  geom_col(color = "black") +
  geom_label(aes(label = NA),
             colour = "white",
             size = 10,
             position = position_stack(vjust = 0.5),
             show.legend = F) +
  coord_polar(theta = "y") +
  guides(fill = guide_legend(title = "State")) +
  scale_fill_viridis_d() + #discrete palette, _c for continuous
  theme_void()
```

The illnesses reported by respondents.
```{r count AD represented, echo = F}
#find types of illnesses represented
ad.cloud <- df.ad %>%
  select(contains("autoimmune_id__"), -c(autoimmune_id___44, autoimmune_id___45, autoimmune_id___120, autoimmune_id___123, autoimmune_id___124, autoimmune_id___135), -contains("factor")) 
ad.labels <- ad.cloud %>%
  get_label 
ad.labels <- gsub("\\(.*", "", ad.labels) %>% #TODO this removes the brackets in the AD labels
  str_trim
ad.cloud <- ad.cloud %>%
  mutate_if(is.character, as.numeric) #for some reason initial ADs were character columns, so convert back
colnames(ad.cloud) <- ad.labels
ad.count <- ad.cloud %>% 
  summarise_if(is.numeric, sum) %>% 
  transpose()
ad.count.df <- as.data.frame(do.call(cbind, ad.count)) %>% 
  rownames_to_column(.) %>% 
  rename(., word = rowname, freq = V1)
ad.count.df$freq <- as.numeric(as.character(ad.count.df$freq))
```

```{r bar plot of ADs, echo = F}
ad.count.ord <- ad.count.df %>%
  filter(freq > 9)%>%
  rename(., Autoimmune_disorder = word) %>%
  arrange(., desc(freq))
#TODO include healthy controls?

ggplot(ad.count.ord, aes(x = freq, y = Autoimmune_disorder)) +
  geom_col(fill = viridis(32)) +
  scale_y_discrete(limits=rev(ad.count.ord$Autoimmune_disorder)) +
  labs(title = NULL,
       x = NULL, 
       y = NULL) +
  scale_x_continuous(expand = c(0, 0), 
                     limits = c(0, 200),
                     breaks = c(0, 20, 40, 60, 80, 100, 120, 140, 160, 180)) +
  theme_bw() +
  theme(plot.title=element_text(size=20, face="bold"),
        axis.title=element_text(size=25),
        axis.text=element_text(size=10, face="bold"))
```

### What does the ME/CFS respondents demographics look like?

What is the number of respondents with ME/CFS?
```{r pull out ME/CFS number, echo = F}
ad.count.ord %>%
    filter(Autoimmune_disorder == "ME/CFS")
```

```{r make df of me info, echo=FALSE}
me.entries <- subset(df.ad, autoimmune_id___55 == 1) %>%
  select(record_id, contains("autoimmune_id___"), contains("chronic___"), -c(autoimmune_id___44, autoimmune_id___45, autoimmune_id___55, autoimmune_id___120, autoimmune_id___123, autoimmune_id___124, autoimmune_id___135, chronic___7,), -contains("factor"))
suppl.df <- data.clean %>%
  select(record_id,
         diseasestat,
         state,
         gender,
         misdiag,
         diagnosis_length,
         year_of_birth,
         self,
         formal)

suppl.df$age <- (2022 - as.numeric(suppl.df$year_of_birth))

me.df <- suppl.df  %>%
  inner_join(me.entries, by="record_id")

me.df <- me.df %>%
  mutate_if(is.character, as.numeric)

me.df <- me.df %>% #prev hist.test
  mutate(gender.id = case_when(
    gender == "1" ~ "Female",
    gender == "2" ~ "Male",
    gender == "3" ~ "Gender fluid",
    gender == "4" ~ "Non-binary",
    gender == "5" ~ "Other",
    gender == "6" ~ "Prefer not to say",
    gender == "NA" ~ "Non response"
  )) %>%
  mutate(disease.id = case_when(
    diseasestat == "0" ~ "Control group",
    diseasestat == "1" ~ "Chronically ill cohort",
    diseasestat == "NA" ~ "Non response"
  )) %>%
  mutate(dia_len_id = case_when(
    diagnosis_length == "2" ~ "Less than six months",
    diagnosis_length == "3" ~ "6 months - 1 year",
    diagnosis_length == "4" ~ "1 - 2 years",
    diagnosis_length == "5" ~ "3 - 4 years",
    diagnosis_length == "6" ~ "4 - 5 years",
    diagnosis_length == "7" ~ "6 - 7 years",
    diagnosis_length == "8" ~ "7 - 8 years",
    diagnosis_length == "9" ~ "9 - 10 years",
    diagnosis_length == "10" ~ "10+ years",
    diagnosis_length == "NA" ~ "Non response"
  ))  %>%
  mutate(misdiag.id = case_when(
    misdiag == "0" ~ "Not misdiagnosed",
    misdiag == "1" ~ "Misdiagnosed",
    misdiag == "NA" ~ "Non response"
  ))

me.df$dia_len_id <- factor(me.df$dia_len_id, levels = c("Non response", 
                                                                      "Less than six months", 
                                                                      "6 months - 1 year", 
                                                                      "1 - 2 years", 
                                                                      "3 - 4 years", 
                                                                      "4 - 5 years", 
                                                                      "6 - 7 years", 
                                                                      "7 - 8 years", 
                                                                      "9 - 10 years", 
                                                                      "10+ years"))
```

What is the age and gender distribution on ME/CFS respondents?
```{r me histogram age, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.cap="Age and gender of respondents with ME/CFS"}
ggplot(me.df, aes(x = age, fill = gender.id, color = gender.id)) +
  geom_histogram(binwidth = 5,
                 alpha = 0.5) +
  scale_x_continuous(breaks = seq(20, 95, by = 10)) +
  scale_y_continuous(breaks = seq(0, 100, by = 10)) +
  theme_bw() +
  labs(title = NULL,
       y = NULL, 
       x = "Age of respondents",
       fill = "Gender") +
  theme(text = element_text(family = "Helvetica-Narrow", face = "bold")) 
``` 
Looking at the age distribution here, it would be relatively easy to age match ME/CFS respondents here to the onek1k cohort whose median age is roughly around 60 years of age.


Where are the ME/CFS respondents from?
```{r figure of ME states,  fig.height = 4, fig.width = 5, fig.align='center', fig.cap="Respondents with ME/CFS by state of residence.", echo=FALSE, warning=FALSE}
### pie chart of states
state.me <- me.df %>%
  count(state) #%>% 
#.[-9, ] #leave in if NAs should be removed
state.me$state2 <- c("ACT", "NSW", "NT", "QLD", "SA", "TAS", "VIC", "WA")

state.me %>% select(-state)
#png("state-summary.png")
ggplot(state.me, aes(x = "", y = n, fill = state2)) +
  geom_col(color = "black") +
  geom_label(aes(label = NA),
             colour = "white",
             size = 10,
             position = position_stack(vjust = 0.5),
             show.legend = F) +
  coord_polar(theta = "y") +
  guides(fill = guide_legend(title = "State")) +
  scale_fill_viridis_d() + #discrete palette, _c for continuous
  theme_void()
```

What's the age and sex distribution of ME/CFS respondents?
```{r me histogram state, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.cap="Gender of respondents with ME/CFS by state"}
state.label <- c("ACT", "NSW", "NT", "QLD", "SA", "TAS", "VIC", "WA")

ggplot(me.df, aes(x = state, fill = gender.id, color = gender.id)) +
  geom_bar(binwidth = 5,
                 alpha = 0.5) +
  scale_x_discrete(labels = state.label) +
#  scale_y_continuous(breaks = seq(0, 100, by = 10)) +
  theme_bw() +
  labs(title = NULL,
       y = NULL, 
       x = "State of residence of ME/CFS respondents",
       fill = "Gender") +
  theme(text = element_text(family = "Helvetica-Narrow", face = "bold")) 
```

What's the misdiagnsosis rate like for ME/CFS  respondents?
```{r me misdia, echo=FALSE, warning=FALSE, fig.cap="Misidagnosis rate of respondents with ME/CFS"}
misd.me <- me.df %>% 
  select(misdiag) %>%
  filter(misdiag == 1) %>%
  count(.)#47
nmis.me <- me.df %>% 
  select(misdiag) %>%
  filter(misdiag == 0) %>%
  count(.)# 34

narp.me <- me.df %>% 
  select(misdiag, self, formal) %>%
  filter(self == 1 | formal == 1) %>%
  filter(is.na(misdiag)) %>%
  select(misdiag) %>%
  count(.) #10

ids.me <- c("Misdiagnosed", "Correct diagnosis", "Missing")
vals.me <- c(misd.me, nmis.me, narp.me)
mis.me <- as.data.frame(cbind(ids.me, vals.me))
mis.me$ids.me  <- as.character(mis.me$ids.me)

#pie chart misdiagnosis
ggplot(mis.me, aes(x = "", y = vals.me, fill = ids.me)) +
  geom_col(color = "black") +
  geom_label(aes(label = NA),
             colour = "white",
             size = 0.1,
             position = position_stack(vjust = 0.5),
             show.legend = F) +
  coord_polar(theta = "y") +
  guides(fill = guide_legend(title = "Diagnosis")) +
  scale_fill_viridis_d(option = "inferno",
                       direction = -1) + #discrete palette, _c for continuous
  theme_void() +
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 15))
```
Interestingly, 45 respondents neither picked the formal nor self-diagnosis sections as a 'yes' so they won't have seen a few of the relevant questions we look at here.

How long does it generally take for ME/CFS patients to receive a diagnosis?
```{r me len dia, echo=FALSE, fig.cap="Time taken for ME/CFS respondents to receive a diagnosis"}
# freqs = plyr::count(cbind(me.df$diagnosis_length.factor, me.df$misdiag) ) 
# testx = spread(freqs, key = "x", value="freq")
# testx[is.na(testx[,1]),1] = "Missing" 
# 
# 
# rownames(testx)  = testx[,1] 
# testx = testx[,-c(1,11)] # remove NA column, and labels 
# testx[is.na(testx)] = 0 
# 
# colnames(testx) = c("Less than six months","6 months - 1 year","1 - 2 years","3 - 4 years","4 - 5 years","6 - 7 years","7 - 8 years","9 - 10 years","10+ years")
# rownames(testx) = c("Correct diagnosis", "Misdiagnosed", "Missing")

# ggplot(me.df,
#        aes(x = dia_len_id,
#            fill = misdiag.id)) +
#   scale_x_discrete(expand = c(0, 0)) +
#   scale_y_continuous(expand = c(0, 0), breaks = seq(0, 15)) +
#   theme_bw() +
#   geom_bar(position = position_dodge(preserve = "single")) +
#   scale_fill_viridis_d(option = "inferno")
# 
# ggplot(me.df, aes(x = dia_len_id, fill = misdiag.id, color = misdiag.id) +
#   geom_histogram(binwidth = 5,
#                  alpha = 0.5) +
#   scale_x_discrete(breaks = seq(20, 95, by = 10)) +
#   scale_y_continuous(breaks = seq(0, 30, by = 5)) +
#   theme_bw() +
#   labs(title = NULL,
#        y = NULL, 
#        x = "Length to diagnosis",
#        fill = "Diagnostic status") +
#   theme(text = element_text(family = "Helvetica-Narrow", face = "bold"))) 
```

Do they usually have ME/CFS in isolation, or other illnesses?
```{r me number of illnesses comorb, echo=FALSE}

```

What are the most common other autoimmune disorders that ME/CFS respondents had?
```{r me number of illnesses, echo=FALSE}
me.cloud <- me.df %>%
  select(contains("autoimmune_id__")) 
me.labels <- me.cloud %>%
  get_label 
me.labels <- gsub("\\(.*", "", me.labels) %>% #TODO this removes the brackets in the AD labels
  str_trim
colnames(me.cloud) <- me.labels
#lables are lost for initial sections, which means they come up as blank #TODO up to here, some fuckery abounds
me.cloud %>% filter(duplicated())

me.count <- me.cloud %>% 
  summarise_if(is.numeric, sum) %>% 
  transpose()
me.count.df <- as.data.frame(do.call(cbind, me.count)) %>% 
  rownames_to_column(.) %>% 
  rename(., word = rowname, freq = V1)
me.count.df$freq <- me.numeric(as.character(me.count.df$freq))

ad.count.ord <- ad.count.df %>%
  filter(freq > 9)%>%
  rename(., Autoimmune_disorder = word) %>%
  arrange(., desc(freq))
#TODO include healthy controls?

ggplot(ad.count.ord, aes(x = freq, y = Autoimmune_disorder)) +
  geom_col(fill = viridis(32)) +
  scale_y_discrete(limits=rev(ad.count.ord$Autoimmune_disorder)) +
  labs(title = NULL,
       x = NULL, 
       y = NULL) +
  scale_x_continuous(expand = c(0, 0), 
                     limits = c(0, 200),
                     breaks = c(0, 20, 40, 60, 80, 100, 120, 140, 160, 180)) +
  theme_bw() +
  theme(plot.title=element_text(size=20, face="bold"),
        axis.title=element_text(size=25),
        axis.text=element_text(size=10, face="bold"))
```


How common are co-morbidities for ME/CFS respondents?
```{r me co-moerbs, echo=FALSE}
como.df.me <- me.df %>%
  select(contains("chronic_"), -chronic___7, -contains("factor"))  #record_id, 
como.labels.me <- como.df.me %>%
  get_label 
como.df.me <- como.df.me %>%
  mutate_if(is.character, as.numeric) #for some reason initial ADs were character columns, so convert back
colnames(como.df.me) <- como.labels.me
como.count.me <- como.df.me %>% 
  mutate_if(is.character, as.numeric) %>%
#  select(como.df, -contains("ecord")) %>%
  summarise_if(is.numeric, sum) %>% 
  transpose()
como.count.df.me <- as.data.frame(do.call(cbind, como.count.me)) %>% 
  rownames_to_column(.) %>% 
  rename(., Comorbidity = rowname, freq = V1)
como.count.df.me$freq <- as.numeric(as.character(como.count.df.me$freq))

como.count.df.me %>% arrange(desc(freq))

#wordcloud2(como.count.df, shape = 'diamond', color = "random-light", backgroundColor = "grey")

##piechart comorbs
# ggplot(como.count.df.me, aes(x = "", y = freq, fill = Comorbidity)) +
#   geom_col(color = "black") +
#   geom_label(aes(label = NA),
#              colour = "white",
#              size = 6,
#              position = position_stack(vjust = 0.5),
#              show.legend = F) +
#   coord_polar(theta = "y") +
#   guides(fill = guide_legend(title = "Co-morbidity")) +
#   scale_fill_viridis_d(option = "inferno") + #discrete palette, _c for continuous
#   theme_void() +
#   theme(legend.title = element_text(size = 14),
#         legend.text = element_text(size = 15))
```